The aims of science and an open science controversy at USEPA

### 2025-04-28 paper/methods.qmd
starting to work on draft for IEEE; AFT format

---
format:
  pdf:
    mainfont: "Times New Roman"
    fontsize: "12pt"
    geometry: 
      - "margin = 1in"
    linestretch: 1.5
---

@@

For Strengthening Transparency, Regulations.gov reports 993,464 "comments received" and 22,390 "comments posted to this docket" and publicly available.  *[TODO: email for clarification on relationship between these numbers]*  It's likely that this disparity is due, in part, to separately enumerating some mass comments that were submitted collectively.  For example, comment 11822 (<https://www.regulations.gov/comment/EPA-HQ-OA-2018-0259-11822>) includes 22,786 individual comments collected by Friends of the Earth (likely using an online form) and submitted as large PDFs, one individual comment per page.

@@

Comments were primarily submitted during two public comment periods, one following the publication of the Notice of Proposed Rulemaking (NPR) on *[date]* and the second in response to the Revised Notice of Proposed Rulemaking (RNPR) on *[date]*.  Comments varied in length dramatically: a few handwritten postcards could not be parsed by OCR and were counted as being 0 words in length, and the longest comment (including the comment text and all attachment text) was 467,917 words long. The median comment was 236 words long, and 95% of comments were 495 words long or less. See figure @fig-date-ecdf.

@@

We defined a model workflow that took the raw text of the comment — comment and attachment text concatenated, as with the NLP tagging — as input.  For processing efficiency, text was truncated after the first 3,000 characters, covering approximately the first 500 words, on the assumption that even long comments would express their support or opposition clearly within the first page or so.  Next, the text was tokenized, stopwords removed *[source]*, and tokens lemmatized.  The resulting token features were hashed to $1024 = 2^10^$ features, with signed binary values (0, +1, -1).  Zero variance features were removed.  Finally, because `support` was heavily imbalanced, during training supporting comments were upsampled using simple resampling.  Use of the `tidymodels` framework ensured that this preprocessing pipeline could be applied exactly to both training and testing data, as well as the full corpus, without any risk of data contamination.

@@

Based on tuning results, we selected a penalty of $\lambda = 0.0385662$ and fit the logistic lasso on the full training data.  This model had a balanced accuracy of 96% and a specificity of 94% on the testing data.  We then used this model to impute dichotomous supporting/opposing codes to the *[full]* corpus of 20.8k comments, without carrying over manual comments.  After imputation, the corpus contained 14,995 opposing comments (72%) and 5,792 supporting comments (28%).  To allow for ambiguous comments, we filtered down to comments where the model was more than 80% confident in its classification (predicted probability of opposition was either greater than 80% or less than 20%).  This filtered subset contained 14,101 opposing comments (74%) and 4,876 supporting comments (26%), for a total of 18,977 (91% of the comments run through imputation).

*[The distribution of document lengths, in words (spaCy-annotated tokens), after coding is shown in fig @fig-len. 11_len.png]*

>>>>

@@

For Strengthening Transparency, Regulations.gov reports 993,464 "comments received" and 22,390 "comments posted to this docket" and publicly available.  As explained in the main text, this disparity is due to the way Regulations.gov counts identical mass comments separately for "comments received" but groups them together for "comments posted to this docket."  For example, comment 11822 (<https://www.regulations.gov/comment/EPA-HQ-OA-2018-0259-11822>) includes 22,786 individual comments collected by Friends of the Earth (likely using an online form) and submitted as large PDFs, one individual comment per page.

@@

Comments were primarily submitted during two public comment periods, one following the publication of the Notice of Proposed Rulemaking (NPR) on 2018-04-30 [@USEPAStrengtheningTransparencyRegulatory2018] and the second in response to the Revised Notice of Proposed Rulemaking (RNPR) on 202-03-03 [@USEPAStrengtheningTransparencyRegulatory2020a].  Comments varied in length dramatically: a few handwritten postcards could not be parsed by OCR and were counted as being 0 words in length, and the longest comment (including the comment text and all attachment text) was 467,917 words long. The median comment was 236 words long, and 95% of comments were 495 words long or less. See figure @fig-date-ecdf.

@@

We defined a model workflow that took the raw text of the comment — comment and attachment text concatenated, as with the NLP tagging — as input.  For processing efficiency, text was truncated after the first 3,000 characters, covering approximately the first 500 words, on the assumption that even long comments would express their support or opposition clearly within the first page or so.  Next, the text was tokenized, stopwords removed *[source]*, and tokens lemmatized.  The resulting token features were hashed to $1024 = 2^{10}$ features, with signed binary values (0, +1, -1).  Zero variance features were removed.  Finally, because `support` was heavily imbalanced, during training supporting comments were upsampled using simple resampling.  Use of the `tidymodels` framework ensured that this preprocessing pipeline could be applied exactly to both training and testing data, as well as the full corpus, without any risk of data contamination.

@@

Based on tuning results, we selected a penalty of $\lambda = 0.0385662$ and fit the logistic lasso on the full training data.  This model had a balanced accuracy of 96% and a specificity of 94% on the testing data.  We then used this model to impute dichotomous supporting/opposing codes to the *[full]* corpus of 20.8k comments, without carrying over manual comments.  After imputation, the corpus contained 14,995 opposing comments (72%) and 5,792 supporting comments (28%).  To allow for ambiguous comments, we filtered down to comments where the model was more than 80% confident in its classification (predicted probability of opposition was either greater than 80% or less than 20%).  This filtered subset contained 14,101 opposing comments (74%) and 4,876 supporting comments (26%), for a total of 18,977 (91% of the comments run through imputation).  The distribution of document lengths is shown in @fig-len.

![Distribution of document lengths, in words (spaCy-annotated tokens), by support/opposition and coding method](../out/11_len.png){#fig-len}

### 2025-04-28 paper/paper.qmd
starting to work on draft for IEEE; AFT format

---
title: "The aims of science and an open science controversy at USEPA"
authors:
  - name: "D. J. Hicks"
    email: "dhicks4@ucmerced.edu"
    affiliations: 
      - id: ucm
        name: "University of California, Merced"
        city: "Merced"
        country: "CA, USA"
    orcid: "0000-0001-7945-4416"
    corresponding: true
  - name: "Emilio J. C. Lobato"
    affiliations:
      - ref: ucm
    orcid: "*[todo]*"
  - name: "Cosmo Campbell"
    affiliations:
      - ref: ucm
  - name: "Joseph Dad"
    affiliations:
      - ref: ucm

@@

format:
  html:
    toc: true
    number-sections: true
  pdf:
    toc: true
    number-sections: true
    link-citations: true
    pdf-engine: "lualatex"
    mainfont: "Times New Roman"
    fontsize: "12pt"
    geometry: 
      - "margin = 1in"
    linestretch: 1.5

@@

*[
- general science-and-values
- aims approach
- Strengthening Transparency
]*

Text mining is an emerging method for empirical philosophy of science.  Broadly, text mining aims to identify patterns in the use of terms across a large collection of documents (called a *corpus*).  While initially developed by computer scientists, text mining methods have been widely adopted by social scientists [@NelsonComputationalGroundedTheory2020; @StoltzMappingTextsComputational2024] and (more contentiously) humanists, under the umbrella of "digital humanities" [@UnderwoodDistantHorizonsDigital2019].

One of the first applications of text mining to philosophy of science was an analysis of Charles Darwin's reading list [@MurdockExplorationExploitationVictorian2017], which used an information-theoretic measure of "surprise" to model Darwin's use of "exploration" and "exploitation" strategies in his reading.  Malaterre and collaborators have reflexively applied one prominent text mining method, topic modeling, to philosophy of science corpora — especially journal archives — to trace developments in the field over time [@MalaterreRevisitingThreeDecades2019; @MalaterreWhatThisThing2019; @MalaterreEightJournalsEight2020; @MalaterreEarlyDaysContemporary2022].  Their most recent work combines machine translation with topic modeling, expanding the scope of their analysis to incorporate multiple languages.  The text mining case studies in @DeBlockDynamicsScienceComputational2022 deploy a variety of methods, including named-entity recognition (NER) and network analysis [@PenceHowNotFight2022] and keyword search to facilitate deep reading [@GinammiBolzanoKantTraditional2022].  @VaesenPotentialSupervisedMachine2022 argues that supervised machine learning approach can incorporate philosophical expertise in ways that topic modeling cannot; we independently adopted a similar approach in part of the current study.

*[methods pieces by Charles?]*

@@

We propose that public comments on high-profile governmental regulatory actions can be apt and convenient corpora for public scientific controversies.  In the United States, the Administrative Procedure Act requires federal government agencies to follow a "notice and comment" process before adopting new or modified regulations *[cite]*.  Agencies are required to publish a Notice of Proposed Rulemaking (NPR), including the draft text of the rule and background information to justify it, and then collect and respond to public comments before finalizing the rule.  Conveniently for our purposes, most comments are made freely and publicly available.  High-profile proposed rules can collect large numbers of comments, from a variety of different groups and perspectives on the issue at hand in the rule, making it apt for understanding how different groups might, for instance, deploy different views of the aims of science.

ST had an exceptionally high profile, with nearly one million comments.^[In the text mining results below, the corpus contains "only" about 22,000 comments.  Regulations.gov distinguishes between "comments posted" and "comments received"; a single comment for the "posted" count can include multiple comments for the "received" count.  For example, the longest comments in the ST corpus comprise tens of thousands of signed electronic form letters.  This aggregation would count as one "posted" comment but tens of thousands of "received" comments.]  We use this substantial corpus to examine how supporters and opponents talk about science and health, finding that opponents talk about health and the environment about as often as they talk about science; while supporters talk exclusively about science, with a distinctive emphasis on a cynical or skeptical framing of the epistemic reliability of the science utilized by USEPA.  We argue that these differences correspond to Hicks' [-@HicksWhenVirtuesAre2022] distinction between broad and narrow views of science.

The bulk of this paper gives a non-technical overview of our text mining methods (@sec-methods-overview) and results (@sec-results).  @sec-methods provides a more technical discussion of our methods, for readers who are familiar with text mining.  In @sec-discussion, we first argue that our empirical results can be fruitfully understood in terms of the two views of the aims of science.  We go on to suggest that, in the context of public discourse, deployment of philosophical ideas should be understood as somewhat opportunistic interpretive frames, rather than authentic expressions of beliefs or deep philosophical commitments.  Finally, we consider the role of advocacy organizations in shaping the content of public scientific controversies, and consider the applicability of a "participatory" model developed in misinformation studies to the case of ST.

@@

All agency-published documents and public comments associated with a proposed rule are collected together in a docket, e.g., EPA-HQ-OA-2018-0259 for Strengthening Transparency, available at <https://www.regulations.gov/docket/EPA-HQ-OA-2018-0259>.  We collected all public comments from this docket in 2020 and 2021, with a final check several months after ST was finalized (in the last few weeks of the Trump administration) and vacated (a few weeks into the Biden administration).

Initial, undirected exploration of the corpus in 2020-2021 by [A1] indicated that (a) there was a qualitatively clear division between supporters and opponents of ST, (b) commenters offered substantive reasons for their position on ST, but (c) opposing comments were much, much more prevalent than supportive comments.  The first point meant that manual qualitative coding could be used to identify supporting and opposing comments; combined with the second point, this meant that the corpus was suitable for contrasting the arguments given on either side of the ST controversy.  But the third point meant that a simple random sample would include very few supporters.  @sec-sampling details the sampling procedure that we used for the manual coding step.

We used a natural language processing (NLP) package for part-of-speech tagging, specifically identifying nouns and adjectives in the comment and attachment text.  (From this point forward, attachments were treated as continuations of comment text, and in what follows references to "comments" include the attachments.)  This let us construct adjective-noun bigrams, such as "public health" or "regulatory science."  Focusing on bigrams based on the nouns "health" and "science" let us greatly reduce the size of the vocabulary — the distinct terms used in a text mining analysis — which in turn greatly reduced the computation time necessary for any individual step.  [A1] had also identified the relationship between science and health, and its potential correspondence to the aims approach, as the central research question of the project. *[also state this earlier]*  Operationalized using science-health bigrams, this difference might show up in differences in noun frequency within or between sides (for example, opponents might use science bigrams more than supporters) or in different adjectives used with the same noun (for example, supporters might use different adjectives to describe health).

@@

```{r}
#| eval: true
#| label: "tbl-n-docs"
#| tbl-cap: "Document counts, by coding method and opposition/support"
#| tbl-subcap:
#|   - "Whole corpus"
#|   - "Comments with science/health bigrams"
#| layout-cols: 2
read_rds(here(out_dir, '09_n_docs.Rds'))
read_rds(here(out_dir, '09_n_docs_bigrams.Rds'))
```

In the manual coding, the 33 "neither" comments were almost all procedural requests to extend the public comment period, with a few comments discussing an issue that was brought up as an example in the first NPR (the linear no-threshold model for radiation hazard) that we did not consider relevant to our analysis.  Because the ML classifier was not trained on these 33 "neither" comments, it forced all such comments into either the "support" or the "oppose" category.  Notably, the comments that were dropped by the "low confidence" filter (the "filtered" coding) are generally procedural requests to extend the public comment period.

@@

There are also notable differences in the overall tone of the adjectives in supporters' and opponents' top bigrams.  Supporters seem to express skepticism or cynicism about the quality of scientific research: science is described as secret, secretive, phony, false, fake, shady, or deceptive.  In the context of these skeptical assessments, seemingly-positive valence bigrams — such as real, true, verifiable, and sound science — might be used as privatives, that is, expressing the idea that actually-existing science is *not* real, true, verifiable, or sound.  A skeptical or cynical assessment of science would provide support for ST insofar as open data would make science less secretive and phony and more verifiable and true, etc.  @HicksOpenScienceReplication2023 argued that there is no empirical evidence of a replication crisis in environmental epidemiology [though see @BagiletEstimatingSmallEffects], and that ST's open data requirements would not mitigate widespread irreplicability even if it were a problem in that field.

@@

```{r}
#| eval: true
#| label: "tbl-keyword"
#| tbl-cap: "Keyword occurrence, by coding method and support. Footnotes indicate regular expressions used for search."
read_rds(here(out_dir, '11_keyword_tab.Rds'))
```

@@

We argue that the results above can be fruitfully understood in terms of *[Hicks']* account of two views of the aims of science.  Specifically, we claim that supporters deployed the narrow view, while opponents deployed the broad view.  On the narrow view of supporters of ST, science has only epistemic aims.  The practical applications of science are at best irrelevant to the standards for good scientific research, and allowing such applications to shape things like data collection and analysis is comparable to — indeed, *is* — research misconduct.  The narrow view's exclusive focus on epistemic aims provides argumentative support for truth-promoting practices, such as those promoted by the open science movement, wherever it is feasible to do so.  Deployment of the narrow view explains why supporters said a great deal about science, but almost nothing about public health and the environment, and even very little about business and the economy.  All of these aspects of environmental policy are irrelevant to the standards for good scientific research.

By contrast, opponents deployed the broad view, on which science has both epistemic and practical aims.  Specifically, they appealed to the practical aims of protecting human health and the environment, raising concerns that ST's open data requirements would frustrate the pursuit of these aims, and was therefore "anti-science" *[Hicks]*.  In this way, the broad view provides an argumentative challenge to ST.  Deployment of the broad view explains why opponents talked about public health and the environment almost as frequently as science itself.

Deployment of the broad view might also explain why opponents said relatively little about business and the economy.  On Hicks' theory of value, protecting human health and the environment are aims of environmental public health, but the impacts of regulation on the economy are still accidents, and thus irrelevant to the standards of good scientific research.  @HicksValuesDisclosuresTrust2022 provide survey evidence that, in the context of chemical regulation, members of the public put more trust in a scientist who discloses public health values than one who does not disclose values or discloses economic values.

@@

\appendix

>>>>

---
title: "The aims of science and an open science controversy at USEPA"
authors:
  - name: "D.J. Hicks"
    email: "dhicks4@ucmerced.edu"
    affiliations: 
      - id: a
        name: "University of California, Merced"
        city: "Merced"
        country: "CA, USA"
    orcid: "0000-0001-7945-4416"
    corresponding: true
  - name: "Emilio J. C. Lobato"
    affiliations:
      - ref: a
    orcid: "0000-0002-3066-2932"
  - name: "Cosmo Campbell"
    affiliations:
      - ref: a
  - name: "Joseph Dad"
    affiliations:
      - ref: a

@@

format:
  html:
    toc: true
    number-sections: true
  pdf:
    toc: false
    number-sections: true
    link-citations: true
    pdf-engine: "lualatex"
    mainfont: "Times New Roman"
    fontsize: "12pt"
    geometry: 
      - "margin = 1.25in"
    linestretch: 2
  aft-pdf:
    keep-tex: true
    link-citations: true
    mathspec: true
    fig.env: "figure*"
    include-in-header:
        - text: |
            \usepackage{pdflscape}
    number-sections: true
    cite-method: citeproc

@@

In this paper, we argue that the aims approach to values in science can provide a useful framework for identifying certain kinds of deep disagreements in public scientific controversies. Specifically, by applying text mining methods to a large collection of public comments on an open data rule at the US Environmental Protection Agency (USEPA), we argue that supporters and opponents of the rule exemplify the two rival views of the aims of science identified by Hicks [-@HicksScientificPracticesTheir2012; -@HicksWhenVirtuesAre2022].

*[
- aims approach in general
- Hicks' two views
]*

## *Strengthening Transparency in Regulatory Science*

*Strengthening Transparency in Regulatory Science* (henceforth Strengthening Transparency or ST) was a rule proposed^[Technically, the rule was finalized and adopted in January 2021, just a few weeks before Trump's first administration ended. The rule was never enforced, and formally vacated in February 2021 by a federal judge on procedural grounds and without objection from the Biden administration. The final title of the rule was *Strengthening Transparency in Pivotal Science Underlying Significant Regulatory Actions and Influential Scientific Information*. For simplicity, I usually refer to it by the original title, and I characterize its effects counterfactually.] by USEPA during the first Trump administration [@USEPAStrengtheningTransparencyRegulatory2018; @USEPAStrengtheningTransparencyPivotal2021]. Strengthening Transparency would have imposed a strong open data and code requirement on any "regulatory science" utilized by USEPA to develop new regulations, generally prohibiting the agency from utilizing any research where the data and analysis code were not publicly available [@HicksWhenVirtuesAre2022; @HicksOpenScienceReplication2023].

At least in the initial public notice, Strengthening Transparency was rationalized by an appeal to the open science movement and as a necessary response to the "replication crisis," a purportedly widespread crisis in which influential and high-profile scientific results often could not be replicated [@USEPAStrengtheningTransparencyRegulatory2018 18769-70].  @HicksOpenScienceReplication2023 argued that, at the time ST was proposed, there was limited evidence that the replication crisis extended beyond a handful of scientific fields, and specifically there was no evidence that the crisis covered environmental epidemiology.

Strengthening Transparency was the culmination of a campaign against "secret science" at USEPA. At least since the 1990s [@LernerRepublicansAreUsing2017], regulated industries have leveled complaints against certain highly influential environmental epidemiological studies [such as @DockeryAssociationAirPollution1993 and @RauhImpactPrenatalChlorpyrifos2006], alleging nonspecific data and analysis problems and demanding access to the "raw data" [@HicksWhenVirtuesAre2022 §2.2]. *[secret science act]*

Strengthening Transparency received a relatively high degree of mainstream news coverage [@HakimPesticideStudiesWon2018; @AchenbachScientistsDecryNew2018; @MufsonEPAExcludedTop2018; @FriedmanEPALimitScience2019; @DennisEPAPushesAhead2019] and was publicly opposed by a number of scientific organizations and environmental advocacy organizations *[cites]*.  Notably, some of the public opponents included prominent advocates of open science *[cites]*. Perhaps the most common argument against ST, as reported in news coverage or made by public figures, was that environmental epidemiological studies are often based on medical records and other sensitive information that legally cannot be made publicly available. Another common concern was that, if the rule was applied retroactively, for studies conducted decades ago the "raw data" might no longer exist [again, such as @DockeryAssociationAirPollution1993 and @RauhImpactPrenatalChlorpyrifos2006].

## Text mining

Text mining is an emerging method for empirical philosophy of science.  Broadly, text mining aims to identify patterns in the use of terms across a large collection of documents (called a *corpus*).  While initially developed by computer scientists, text mining methods have been widely adopted by both social scientists [@NelsonComputationalGroundedTheory2020; @StoltzMappingTextsComputational2024] and — under the umbrella of "digital humanities" — humanists [@UnderwoodDistantHorizonsDigital2019].

One of the first applications of text mining to philosophy of science was an analysis of Charles Darwin's reading list [@MurdockExplorationExploitationVictorian2017], which used an information-theoretic measure of "surprise" to model Darwin's use of "exploration" and "exploitation" strategies in his reading.  Malaterre and collaborators have reflexively applied one prominent text mining method, topic modeling, to philosophy of science corpora — especially journal archives — to trace developments in the field over time [@MalaterreRevisitingThreeDecades2019; @MalaterreWhatThisThing2019; @MalaterreEightJournalsEight2020; @MalaterreEarlyDaysContemporary2022].  Their most recent work combines machine translation with topic modeling, expanding the scope of their analysis to incorporate multiple languages.  @HicksRaceScienceMainstream2024 use agnotology as a theoretical framework for a text mining analysis of race science in mainstream psychology. The text mining case studies in @DeBlockDynamicsScienceComputational2022 deploy a variety of methods, including named-entity recognition (NER) and network analysis [@PenceHowNotFight2022] and keyword search to facilitate deep reading [@GinammiBolzanoKantTraditional2022].  @VaesenPotentialSupervisedMachine2022 argues that supervised machine learning approach can incorporate philosophical expertise in ways that topic modeling cannot; we independently adopted a similar approach in part of the current study.

@@

We propose that public comments on high-profile governmental regulatory actions such as Strengthening Transparency can be apt and convenient corpora for understanding the publics involved in public scientific controversies.  In the United States, the Administrative Procedure Act requires federal government agencies to follow a "notice and comment" process before adopting new or modified regulations *[cite]*.  Agencies are required to publish a Notice of Proposed Rulemaking (NPR), including the draft text of the rule and background information to justify it, and then collect and respond to public comments before finalizing the rule.  Conveniently for our purposes, most comments are made freely and publicly available.  High-profile proposed rules can collect large numbers of comments, from a variety of different groups and perspectives on the issue at hand in the rule, making it apt for understanding how different groups might, for instance, deploy different views of the aims of science.

Most likely due to the mainstream news coverage, ST had an exceptionally high profile, with nearly one million comments submitted.^[In the text mining results below, the corpus contains "only" about 22,000 comments.  Regulations.gov distinguishes between "comments posted" and "comments received"; a single comment for the "posted" count can include multiple comments for the "received" count.  For example, the longest comments in the ST corpus comprise tens of thousands of signed electronic form letters.  This aggregation would count as one "posted" comment but tens of thousands of "received" comments.]  We use this substantial corpus to examine how supporters and opponents talk about science and health, finding that opponents talk about health and the environment about as often as they talk about science; while supporters talk exclusively about science, with a distinctive emphasis on a cynical or skeptical framing of the epistemic reliability of the science utilized by USEPA.

We argue that these differences between opponents and supporters correspond to Hicks' [-@HicksWhenVirtuesAre2022] distinction between broad and narrow views of science.  *[more]*

@sec-methods-overview gives a non-technical overview of our text mining methods; @sec-methods provides a more technical discussion, for readers who are familiar with text mining.  @sec-results reports the empirical results of the analysis. In @sec-discussion, we first argue that our empirical results can be fruitfully understood in terms of the two views of the aims of science.  We go on to suggest that, in the context of public discourse, deployment of philosophical ideas should be understood as somewhat opportunistic interpretive frames, rather than authentic expressions of beliefs or deep philosophical commitments.  Finally, we consider the role of advocacy organizations in shaping the content of public scientific controversies, and consider the applicability of a "participatory" model developed in misinformation studies to the case of ST.

@@

All agency-published documents and public comments associated with a proposed rule are collected together in a docket, e.g., EPA-HQ-OA-2018-0259 for Strengthening Transparency, available at <https://www.regulations.gov/docket/EPA-HQ-OA-2018-0259>.  [A1] collected all public comments from this docket in 2020 and 2021, with a final check several months after ST was finalized (in the last few weeks of the Trump administration) and vacated (a few weeks into the Biden administration).

Initial, undirected exploration of the corpus in 2020-2021 by [A1] indicated that (a) there was a qualitatively clear division between supporters and opponents of ST, (b) commenters offered substantive reasons for their position on ST, (c) these reasons often connected science to public health, but (d) opposing comments were much, much more prevalent than supportive comments.  The point (a) meant that manual qualitative coding could be used to identify supporting and opposing comments; combined with points (b) and (c), this meant that the corpus was likely apt for contrasting the arguments given on either side of the ST controversy, and especially the way they connected (or not) epistemic and pragmatic aims.  But the third point meant that a simple random sample would include very few supporters.  @sec-sampling details the sampling procedure that we used for the manual coding step.

We used a natural language processing (NLP) package for part-of-speech tagging, specifically identifying nouns and adjectives in the comment and attachment text.  (From this point forward, attachments were treated as continuations of comment text, and in what follows references to "comments" include the attachments.)  This let us construct adjective-noun bigrams, such as "public health" or "regulatory science."  Focusing on bigrams based on the nouns "health" and "science" let us greatly reduce the size of the vocabulary — the distinct terms used in a text mining analysis — which in turn greatly reduced the computation time necessary for any individual step.  [A1] had also identified the relationship between science and health, and its potential correspondence to the aims approach, as the central research question of the project.  Operationalized using science-health bigrams, this difference might show up in differences in noun frequency within or between sides (for example, opponents might use science bigrams more than supporters) or in different adjectives used with the same noun (for example, supporters might use different adjectives to describe health).

@@

```{r}
#| eval: true
#| label: "tbl-n-docs"
#| tbl-cap: "Document counts, by coding method and opposition/support"
#| tbl-subcap:
#|   - "Whole corpus"
#|   - "Comments with science/health bigrams"
#| layout-cols: 2
read_rds(here(out_dir, '09_n_docs.Rds'))
# read_rds(here(out_dir, '09_n_docs_bigrams.Rds'))
```

In the manual coding, the 33 "neither" comments were almost all procedural requests to extend the public comment period, with a few comments discussing an issue that was mentioned as an example in the first NPR (the linear no-threshold model for radiation hazard) that we did not consider relevant to our analysis.  Because the ML classifier was not trained on these 33 "neither" comments, it forced all such comments into either the "support" or the "oppose" category.  Notably, the comments that were dropped by the "low confidence" filter (the "filtered" coding) are generally procedural requests to extend the public comment period.

@@

There are also notable differences in the overall tone of the adjectives in supporters' and opponents' top bigrams.  Supporters seem to express skepticism or cynicism about the quality of scientific research: science is described as secret, secretive, phony, false, fake, shady, or deceptive.  In the context of these skeptical assessments, seemingly-positive valence bigrams — such as real, true, verifiable, and sound science — might be used as privatives, that is, expressing the idea that actually-existing science is *not* real, true, verifiable, or sound.  A skeptical or cynical assessment of science would provide support for ST insofar as open data would make science less secretive and phony and more verifiable and true, etc.  @HicksOpenScienceReplication2023 argued that there is no empirical evidence of a replication crisis in environmental epidemiology [though see @BagiletEstimatingSmallEffects *[cite as well in intro]*], and that ST's open data requirements would not mitigate widespread irreplicability even if it were a problem in that field. @HicksDevelopingMeasuresPublic2024 report preliminary evidence that cynicism is a better predictor of generalized trust in science than the value-free ideal.

@@

```{=latex}
\begin{landscape}
```
```{r}
#| eval: true
#| label: "tbl-keyword"
#| tbl-cap: "Keyword occurrence, by coding method and support. Footnotes indicate regular expressions used for search."
#| tbl-align: center
read_rds(here(out_dir, '11_keyword_tab.Rds'))
```
```{=latex}
\end{landscape}
```

@@

We argue that the results above can be fruitfully understood in terms of @HicksWhenVirtuesAre2022 account of two views of the aims of science.  Specifically, we claim that supporters deployed the narrow view, while opponents deployed the broad view.

On the narrow view of supporters of ST, science has only epistemic aims.  The practical applications of science are at best irrelevant to the standards for good scientific research, and allowing such applications to shape things like data collection and analysis is comparable to — indeed, *is* — research misconduct.  The narrow view's exclusive focus on epistemic aims provides argumentative support for truth-promoting practices, such as those promoted by the open science movement, wherever it is feasible to do so.  Deployment of the narrow view explains why supporters said a great deal about science, but almost nothing about public health and the environment, and even very little about business and the economy.  All of these aspects of environmental policy are irrelevant to the standards for good scientific research.

By contrast, opponents of ST deployed the broad view, on which science has both epistemic and practical aims.  Specifically, they appealed to the practical aims of protecting human health and the environment, raising concerns that ST's open data requirements would frustrate the pursuit of these aims, and was therefore "anti-science" [a primary goal of @HicksWhenVirtuesAre2022 is to develop a robust version of this argument].  In this way, the broad view provides an argumentative challenge to ST.  Deployment of the broad view explains why opponents talked about public health and the environment almost as frequently as science itself.

Deployment of the broad view might also explain why opponents said relatively little about business and the economy.  On Hicks' theory of value, protecting human health and the environment are aims of environmental public health, but the impacts of regulation on the economy are still accidents, and thus irrelevant to the standards of good scientific research.  @HicksValuesDisclosuresTrust2022 provide survey evidence that, in the context of chemical regulation, members of the public — including political conservatives — put more trust in a scientist who discloses public health values than one who does not disclose values or discloses economic values.

@@

# References

::: {#refs}
:::

\appendix
\clearpage
\pagenumbering{arabic}
\renewcommand*{\thepage}{S\arabic{page}}
\renewcommand\thefigure{S\arabic{figure}}    
\setcounter{figure}{0} 
\renewcommand\thetable{S\arabic{table}}    
\setcounter{table}{0}
\renewcommand*{\thesection}{S\arabic{section}}
